MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-28 paper.Rmd
New reference.

<!-- Define some macros to use later -->
[link-cran]:           https://cran.r-project.org
[link-ieatools]:       https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:        https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:            https://www.ilo.org/
[link-fao]:            https://www.fao.org/
[link-matsbyname]:     https://CRAN.R-project.org/package=matsbyname
[link-matsindf]:       https://CRAN.R-project.org/package=matsindf
[link-mwtools]:        https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:       https://github.com/energyeconomydecoupling/PFUSetup
[link-pfudatabase]:    https://github.com/energyeconomydecoupling/PFUDatabase
[link-pfuaggdatabase]: https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-rclabels]:       https://CRAN.R-project.org/package=RCLabels
[link-recca]:          https://github.com/MatthewHeun/Recca
[link-targets]:        https://docs.ropensci.org/targets
[link-tidyverse]:      https://www.tidyverse.org

@@

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.
Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
benefit from the 
[PFUSetup][link-pfusetup] package [@Heun-pfusetup:2023], which
identifies storage locations for input and output data.

@@

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts [IEA WEEB][link-ieaweeb] data to RUVY matrices in [matsindf][link-matsindf] data frames |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to RUVY matrices of human and animal muscle work in [matsindf][link-matsindf] data frames |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Identifies input and output locations for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUDatabase][link-pfudatabase]       | Provides a [targets][link-targets] pipeline to create a data frame of RUVY matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | Provides a [targets][link-targets] pipeline to aggregate RUVY matrices |

@@

>>>>

<!-- Define some macros to use later -->
[link-cran]:             https://cran.r-project.org
[link-ieatools]:         https://github.com/MatthewHeun/IEATools
[link-ieaweeb]:          https://www.iea.org/data-and-statistics/data-product/world-energy-balances
[link-ilo]:              https://www.ilo.org/
[link-fao]:              https://www.fao.org/
[link-matsbyname]:       https://CRAN.R-project.org/package=matsbyname
[link-matsindf]:         https://CRAN.R-project.org/package=matsindf
[link-mwtools]:          https://github.com/EnergyEconomyDecoupling/MWTools
[link-pfusetup]:         https://github.com/energyeconomydecoupling/PFUSetup
[link-pfudatabase]:      https://github.com/energyeconomydecoupling/PFUDatabase
[link-pfuaggdatabase]:   https://github.com/EnergyEconomyDecoupling/PFUAggDatabase
[link-pfupipelinetools]: https://github.com/EnergyEconomyDecoupling/PFUPipelineTools
[link-rclabels]:         https://CRAN.R-project.org/package=RCLabels
[link-recca]:            https://github.com/MatthewHeun/Recca
[link-targets]:          https://docs.ropensci.org/targets
[link-tidyverse]:        https://www.tidyverse.org

@@

A second [targets][link-targets] pipeline 
in the [PFUAggDatabase][link-pfuaggdatabase] package [@Heun-PFUAggDatabase:2023]
aggregates ECCs
(a) by region 
(continents and world),
(b) by energy carrier (product) category 
(e.g., Coal and coal products, 
Low-, Medium-, and High-temperature heat, etc.), 
(c) by energy conversion machines (industries) and end use sectors
(e.g., Residential, Transport, etc.), and
(d) to primary, final, and useful (PFU) stages.
The [PFUAggDatabase][link-pfuaggdatabase]
pipeline uses the [Recca][link-recca] package extensively.

Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
benefit from the 
[PFUSetup][link-pfusetup] [@Heun-PFUSetup:2023] and
[PFUPipelineTools][link-pfupipelinetools] [@Heun-PFUPipelineTools:2023]
packages. 
[PFUSetup][link-pfusetup] identifies storage locations 
for pipeline input and output data.
[PFUPipelineTools][link-pfupipelinetools] provides functions and constants
common to both pipelines.

@@

| Package | Purpose |
|:--------|:--------|
| [IEATools][link-ieatools]             | Converts [IEA WEEB][link-ieaweeb] data to RUVY matrices in [matsindf][link-matsindf] data frames |
| [MWTools][link-mwtools]               | Converts [ILO][link-ilo] and [FAO][link-fao] data to RUVY matrices of human and animal muscle work in [matsindf][link-matsindf] data frames |
| [Recca][link-recca]                   | Performs `R` energy conversion chain analysis |
| [PFUSetup][link-pfusetup]             | Identifies input and output locations for the [PFUDatabase][link-pfudatabase] and [PFUAggDatabase][link-pfuaggdatabase] pipelines |
| [PFUPipelineTools][link-pfupipelinetools] | Provides basic functionality for all PFU pipelines |
| [PFUDatabase][link-pfudatabase]       | Provides a [targets][link-targets] pipeline to create a data frame of RUVY matrices |
| [PFUAggDatabase][link-pfuaggdatabase] | Provides a [targets][link-targets] pipeline to aggregate RUVY matrices |

@@

**** Change to Zenodo DOIs for all package references?. ****
